### 2020-04-16 survival.tex
removed censors from pdf plot

% !TEX root = main.tex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Survival Analysis
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Survival Analysis}
\label{section:survival}

>>>>

% !TEX root = main.tex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Survival Analysis
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Survival Analysis}
\label{section:survival}
The construction of a GPU life time is more complex than it initially
appears because the units are observed only at reboot time, because
most units were proactively replaced to prevent failure, and because
some units continue in operation after OTB and DBE events (a second
reboot may be successful).

A unit that experiences at least one OTB or DBE event and is removed
from the system is considered failed and its operation time until the
last seen time is taken as its life time. Although most failed units
experience one of these events at the last seen time, this is
imperfect because some units experience OTB or DBE events at a time
different from its last seen time. We found this definition of life
time the most pragmatic for the study with few imperfect
observations. One exception is if the last seen time is the final
Titan shutdown time, in which case such a unit is not considered
failed.

A key concept in survival analysis and in reliability analysis is
censoring, which is about using information from study subjects whose
exact failure times are not available or that have not failed. This
applies to our study because of proactive GPU replacement before
failure, because most units were still in operation when the system
was shut down, and also because of observation only at inspection
times (reboots). We use censoring concepts on the proactive
replacements and units still in operation at the end. This allows us
to use all of the GPU life time data, including units that did not
fail. But we ignore the inspection time censoring, treating removal
times as exact failure times to reduce the complexity of this
analysis. We expect that because of the volume of data, this would
hardly make a difference in our conclusions.
